---
title: "Campaign Travel Analysis"
description: |
  In this post I hope to demosntrate a few trends in travel for candidates in the 2020 Presidential Election.
author:
  - name: Dylan Lucko
    url: https://dylanlucko.com
date: 04-30-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

Candidates attend a lot of events; here are a few trends...

The chart below depicts the number of trips to events that Kamala Harris took during her campaign. The number of trips per month plateaus around 8/month with a sudden drop off after August. The drop of is largely due to her dropping out of the presidential race and transitioning to Joe Biden's VP.

```{r}
library(tidyverse)
library(lubridate)
library(DT)
library(plotly)

events <- readRDS("~/Documents_1/Spring 2021/Data Journalism/dylan_lucko_site/events_saved.rds")

events_month <- events %>% 
  mutate(month(date))

kamala_months <- events_month %>% 
  filter(cand_lastname== "Harris") %>% 
  #group_by (month(date)) %>% 
  count(month = month(date))


mychart1<-kamala_months %>% 
  plot_ly(x = ~month, 
          y = ~n,
          type = "bar")
mychart1<- mychart1 %>% 
  layout(title= "Total Trips by Harris each Month")

mychart1
```

```{r}


```

The following chart shows the total trips by all candidates to New Hampshire. A possible explanation is that once the NH primary ended, trips began to subside


```{r}
library(tidyverse)
library(lubridate)
library(DT)
library(plotly)

events_month_2 <- events %>% 
  mutate(month(date))

eventsNH <- events_month_2 %>% 
  filter(state == "NH") %>% 
  count(month = month(date))

mychart2<-eventsNH %>% 
  plot_ly(x = ~month, 
          y = ~n,
          type = "bar")
mychart2<- mychart2 %>% 
  layout(title= "Total Trips to New Hampshire by all Candidates")
mychart2

```


The chart below shows the total number of trips Bernie Sanders took during his Election Campaign


```{r}
library(tidyverse)
library(lubridate)
library(DT)
library(plotly)

events <- readRDS("~/Documents_1/Spring 2021/Data Journalism/dylan_lucko_site/events_saved.rds")

events_month_s<- events %>% 
  mutate(month(date))

sanders_months <- events_month_s %>% 
  filter(cand_lastname== "Sanders") %>% 
  #group_by (month(date)) %>% 
  count(month = month(date))


mychart5<-sanders_months %>% 
  plot_ly(x = ~month, 
          y = ~n,
          type = "bar")
mychart5<- mychart5 %>% 
  layout(title= "Total Trips by Sanders each Month")

mychart5
```




The chart below shows the total number of trips Joe Biden took during his Election Campaign



```{r}
library(tidyverse)
library(lubridate)
library(DT)
library(plotly)
events <- readRDS("~/Documents_1/Spring 2021/Data Journalism/dylan_lucko_site/events_saved.rds")

events_month_B<- events %>% 
  mutate(month(date))

biden_months <- events_month_B %>% 
  filter(cand_lastname== "Biden") %>% 
  #group_by (month(date)) %>% 
  count(month = month(date))


mychart6<-biden_months %>% 
  plot_ly(x = ~month, 
          y = ~n,
          type = "bar")
mychart6<- mychart6 %>% 
  layout(title= "Total Trips by Biden each Month")

mychart6
```


